---
title: "resumen gender_gap"
output: html_document
---

```{r setup, include=FALSE}
# Setip del notebook
if(!require("knitr")){
  install.packages("knitr")
  library(knitr)
}
if (!'.git' %in% dir(all.files = T)) {
  opts_knit$set(root.dir = "../../")
}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```


```{r init, include=FALSE,echo=FALSE}
source("init.R")
safeLibrary(rpart)
safeLibrary(rattle)
safeLibrary(h2o)
safeLibrary(tidyverse)
safeLibrary(broom)
safeLibrary(ggthemes)
safeLibrary(h2o)
h2o.init()

dataset = readRDS("data/clean/03_ready.rds")
```

# Inicial

Descripcion del dataset

```{r}
aux = dataset %>% 
  group_by(Male) %>% 
  summarise(salario = mean(ConvertedSalary,na.rm=T),
            number = n()) %>% 
  filter(!is.na(Male))

ggplot(aux,(aes(Male,salario))) + geom_bar(stat = 'identity', fill = 'dark orange') + ggtitle('Salario Promedio por Genero') + scale_fill_tableau() 
```

```{r}
ggplot(filter(dataset,!is.na(Male)),aes(ConvertedSalary,group = Male, fill = Male)) + 
  geom_density(alpha= 0.3,kernel = 'epanechnikov') + 
  ggtitle('Distribucion de Sueldo por Genero')  + 
  scale_fill_tableau() 
```
```{r}
ggplot(filter(dataset,!is.na(Male)),aes(log10(ConvertedSalary),group = Male, fill = Male)) + 
  geom_density(alpha= 0.3,kernel='epanechnikov') + 
  ggtitle('Distribucion de Log Sueldo por Genero')  + 
  scale_fill_tableau() 
```

```{r}
t.test(ConvertedSalary ~ Male, filter(dataset,!is.na(Male)),alternative = 'less')
```


```{r}
ggplot(aux,(aes(Male,number))) + geom_bar(stat = 'identity', fill = 'dark orange') + ggtitle('Tamaño de Muestra') + scale_fill_tableau() 
```

# Metodología
me guiare por los modelos, en vez de buscar.

# Descriptivos

## Arbol

### Salario
```{r}
fitTree = rpart(ConvertedSalary ~ .,dataset)
fancyRpartPlot(fitTree)
```

* OperatingSystem,What is the primary operating system in which you work?
* AssessBenefits2,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Stock options or shares"
* YearsCodingProf,For how many years have you coded professionally (as a part of your work)?

Notese que tambien está: YearsCoding,"Including any education, for how many years have you been coding?" y no entró al modelo

```{r}
aux = dataset %>% 
  group_by(Male) %>% 
  summarise(YearsCodingProf = mean(YearsCodingProf,na.rm=T),
            AssessBenefits2 = mean(AssessBenefits2,na.rm=T),
            number = n()) %>% 
  filter(!is.na(Male))

ggplot(aux,(aes(Male,YearsCodingProf))) + geom_bar(stat = 'identity', fill = 'dark orange') + ggtitle('Años Promedio Programando')
```

```{r}
ggplot(aux,(aes(Male,AssessBenefits2))) + geom_bar(stat = 'identity', fill = 'dark orange') + ggtitle('Preferencia por Acciones de Empresa, Menor es Mayor Preferencia')
```

```{r}
aux = dataset %>%
  filter(!is.na(OperatingSystem) & !is.na(Male) ) %>% 
  group_by(Male,OperatingSystem) %>% 
  summarise(number = n()) %>% 
  group_by(Male) %>% 
  mutate(os_portion = number/sum(number))

ggplot(aux,aes(Male,os_portion, fill = OperatingSystem)) + geom_bar(position = 'stack',stat = 'identity') +
  ggtitle('Porcion de Sistema operativo por Genero') + scale_fill_tableau() 
```


### Genero

```{r}
fitTree = rpart(Male ~ .,dataset, cp = 0.008)
fancyRpartPlot(fitTree) 
```

* YearsCodingProf,For how many years have you coded professionally (as a part of your work)?
* AssessJob9,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The diversity of the company or organization"
* Hobby,Do you code as a hobby?

## Random Forest, Iportancia Variables
```{r}
importance = readRDS('data/models/importance_salary.RDS')
importance = head(importance,10)
ggplot(importance,aes(variable,scaled_importance)) + 
  geom_bar(stat = 'identity',fill='dark orange') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
aux = dataset %>% 
  group_by(Male) %>% 
  summarise(YearsCoding = mean(YearsCoding,na.rm=T),
            YearsCodingProf = mean(YearsCodingProf,na.rm=T),
            Age = mean(Age,na.rm=T),
            number = n()) %>% 
  filter(!is.na(Male))
ggplot(aux,aes(Male,Age)) + geom_bar(stat = 'identity',fill='dark orange') + ggtitle('Edad por Genero')
```

```{r}
ggplot(aux,aes(Male,YearsCoding)) + geom_bar(stat = 'identity',fill='dark orange') + ggtitle('Años Programando por Genero')
```
 
```{r}
aux = aux %>% 
  select(-number,-Male) %>% 
  summarize_all(diff) %>% 
  gather(Variable,Difference)
ggplot(aux,aes(Variable,Difference)) + geom_bar(stat='identity',fill='dark orange') +ggtitle('Diferencia entre años Hombre y Mujer')
```

```{r}
aux = dataset %>% 
  filter(!is.na(Male) & !is.na(Age) & Age > 20  & Age < 60) %>% 
  group_by(Male,Age) %>% 
  summarize(YearsCodingProf = mean(YearsCodingProf,na.rm = T))
ggplot(aux,aes(Age,YearsCodingProf,group = Male, color = Male)) + geom_line(size=2) + ggtitle('Años de experiencia laboral vs Edad')
```
```{r}
ggplot(filter(dataset,!is.na(Male)),aes(YearsCodingProf,group = Male, fill = Male)) + 
  geom_density(alpha= 0.3) + 
  ggtitle('Distribucion de Años de Experiencia por Genero')  + 
  scale_fill_tableau() 
```
```{r}
aux = dataset %>% 
  filter(!is.na(Male) & !is.na(YearsCoding)) %>% 
  group_by(Male,YearsCodingProf) %>% 
  summarize(ConvertedSalary = mean(ConvertedSalary,na.rm = T),
            q = n()) %>% 
  filter(q >15)
ggplot(aux,aes(YearsCodingProf,ConvertedSalary,group = Male, color = Male)) + geom_line(size=2) + ggtitle('Sueldo vs Años de experiencia Laboral')
```


```{r}
aux = dataset[,c('Male','YearsCoding','ConvertedSalary')] %>% 
  na.omit()
summary(lm(ConvertedSalary ~ YearsCoding + Male,aux))
```

```{r}
aux = dataset %>% 
  mutate(DevType_Engineering.manager = DevType_Engineering.manager==1) %>% 
  group_by(DevType_Engineering.manager) %>% 
  summarise(ConvertedSalary = mean(ConvertedSalary,na.rm = T))
ggplot(aux,aes(DevType_Engineering.manager,ConvertedSalary)) + geom_bar(stat='identity',fill='dark orange') +ggtitle('Sueldo Promedio Engineering Manager vs Resto')
```


```{r}
aux = dataset %>% 
  group_by(Male,DevType_Engineering.manager) %>% 
  summarise(number = n()) %>% 
  group_by(Male) %>% 
  mutate(portion = number/sum(number)) %>% 
  filter(!is.na(Male) & DevType_Engineering.manager)
ggplot(aux,aes(Male,portion)) + geom_bar(stat='identity',fill='dark orange') +ggtitle('Porcion de Engineering Manager por Genero')
```

```{r}
fitTree = rpart(DevType_Engineering.manager ~ .,select(dataset,
                                                       -ConvertedSalary,
                                                       -DevType_Product.manager,
                                                       -DevType_Csuite.executive.CEO.CTO.etc,
                                                       -HopeFiveYears), cp = 0.008)
fancyRpartPlot(fitTree) 
```
```{r}
aux = dataset %>% 
  group_by(Male) %>% 
  summarise(PlatformWorkedWith_AWS = mean(PlatformWorkedWith_AWS,na.rm=T),
            number = n()) %>% 
  filter(!is.na(Male))
ggplot(aux,aes(Male,PlatformWorkedWith_AWS)) + geom_bar(stat = 'identity',fill='dark orange') + ggtitle('Trabajo con AWS por Genero')
```


# Simulación
```{r,echo=FALSE,include=FALSE}
dataset = readRDS("data/clean/03_ready.rds")
salary_fit = h2o.loadModel('./data/models/salary_balanced')
dataset = mutate_if(dataset,is.ordered,as.character)
dataset.h2o = as.h2o(dataset)
dataset = bind_cols(dataset, as.data.frame(predict(salary_fit,dataset.h2o)) )
```

```{r}
dataset %>% 
  mutate(scr = (ConvertedSalary-mean(ConvertedSalary))^2,
         error = (ConvertedSalary-as.numeric(predict))^2) %>% 
  summarize(1-sum(error)/sum(scr))
```

```{r}
dataset %>% 
  filter(!is.na(Male)) %>% 
  group_by(Male) %>% 
  mutate(scr = (ConvertedSalary-mean(ConvertedSalary))^2,
         error = (ConvertedSalary-as.numeric(predict))^2) %>% 
  summarize(1-sum(error)/sum(scr))
```
```{r,echo=FALSE,include=FALSE}
dataset_op_sex = mutate(dataset,Male = !Male)
dataset_op_sex.h2o = as.h2o(dataset_op_sex)
dataset = bind_cols(dataset, as.data.frame(predict(salary_fit,dataset_op_sex.h2o)) )
dataset = rename(dataset,
                 estimado = predict,
                 sexo_opuesto = predict1)
```

```{r}
aux = dataset %>% 
  filter(!is.na(Male)) %>% 
  group_by(Male) %>% 
  summarize(estimado = mean(as.numeric(estimado)),
            sexo_opuesto = mean(as.numeric(sexo_opuesto))
  ) 
tidy_aux = aux %>% gather(escenario,sueldo_promedio,-Male)
ggplot(tidy_aux,aes(Male,sueldo_promedio,fill= escenario)) + geom_bar(stat='identity', position='dodge') +ggtitle('Sueldo estimado vs Sueldo Estimado con genero Opuesto')
```

```{r}
aux
```

